Long-range correlations in high-multiplicity proton--proton collisions at \s~=~\unit[13]{TeV}

### 2019-07-13 paper.tex
Test

%QCD has been studied through particles produced in heavy ion collisions. Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions. One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle. Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant. 
\section{Experimental setup}
Collisions of proton and proton were provided by the LHC for a few years from 2015 to 2018 with various energy during Run2 period. The used beam energies were \unit[6.5]{TeV} for both protons so that center-of-mass energy is \unit[13]{TeV}. Among data from pp collisions at \unit[13]{TeV}, This paper shows the results with 2016 to 2017 data set whose total cross section corresponds to xxx. 
Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref(?). The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively. The VZERO provides trigger and event characterization with respect to particle-multiplicity. The ITS is composed of three subsystem, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD). Each subsystem consists of two layers with an acceptance of $|\eta|<$1.95, $|\eta|<$1.xx and $|\eta|<$1.xx. The TPC, which is operated inside a solenoidal magnetic field of 0.5 T, have an acceptance of $|\eta|<$0.9 for tracks reaching the outer radius of the TPC. In pp collisions, trigger requirement is fulfilled by the combination of SPD, VZERO-A or VZERO-C.

\section {Data sample and analysis}

>>>>

%QCD has been studied through particles produced in heavy ion collisions. Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions. One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle. Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.

\section{Experimental setup}
Collisions of proton and proton were provided by the LHC for a few years from 2015 to 2018 with various energy during Run2 period. The used beam energies were \unit[6.5]{TeV} for both protons so that center-of-mass energy is \unit[13]{TeV}. Among data from pp collisions at \unit[13]{TeV}, This paper shows the results with 2016 to 2017 data set whose total cross section corresponds to xxx. 
Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref(?). The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively. The VZERO provides trigger and event characterization with respect to particle-multiplicity. The ITS is composed of three subsystem, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD). Each subsystem consists of two layers with an acceptance of $|\eta|<$1.95, $|\eta|<$1.xx and $|\eta|<$1.xx. The TPC, which is operated inside a solenoidal magnetic field of 0.5 T, have an acceptance of $|\eta|<$0.9 for tracks reaching the outer radius of the TPC. In pp collisions, trigger requirement is fulfilled by the combination of SPD, VZERO-A or VZERO-C.

\section {Event and track selection}
Several event selections have been applied to the data set to reject bad signals. Multiple collisions in the same time(<100 ns) is tagged as "Pileup", which is detected by SPD. The Pileup events have been rejected from the present analysis. Primary vertex range has been chosen as $|z_{\rm{vtx}}|<$8 cm to keep higher tracking efficiency  in large $\eta$ region. The event classes are separated through charged particle-multiplicity using VZERO. The analysis uses ITS and TPC to reconstruct the track of the charged particle. The reconstructed tracks have been selected with $|\eta|<$0.9 and $\it{p}_{\rm{T}}>$0.2 GeV/\it{c}\rm{}. The efficiency of track reconstructed has been estimated from a Monte Carlo(MC) simulation using PYTHIA event generator.

\section {Analysis}
The two-particle angular correlation between trigger particle and associated particle has been measured as function of relative pseudo-rapidity versus relative azimuthal angle. Two particles constructing the correlation are defined as the trigger particle and the associated particle by considering magnitude of transverse momentum of two particles to be $\it{p}_{\rm{T}}^{\rm{trig}}>\it{p}_{\rm{T}}^{\rm{assoc}}$. The correlation takes the number of the trigger particles into its denominator to make the correlation present the associated yield.
